Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-31 automatica/paper.tex
overall paper

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
\caption{Phases of the controller synthesis}
\label{fig:synthesis-flow}
\end{figure*}

The implementation of the proposed methodology for synthesis of digital controls for physical plants is based on the Digital-System Synthesizer 
(DSSynth) tool~\cite{DBLP:conf/kbse/AbateBCCCDKKP17}, 
which can be split into two main stages: manual and automated, as illustrated in Fig.~\ref{fig:synthesis-flow} and detailed next.

In Step~1, the user selects the system representation, which can be a transfer function or a state-space model.  
In Step~2, the plant (e.g., in the form of Equation~\eqref{eq:ode1}) is provided~\cite{astrom1997computer}.  
Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user, i.e., 
the finite precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
or half- and single-precision when using floating-point arithmetic, 
as well as the input range.  
% This input, provided by the user, is a specification of the physical plant.

In the second stage, 
the automated synthesis process starts with Step~A, where the
\tool~translates the model specification into an ANSI-C program.  
In Step~B, the proposed CEGIS engine is invoked to synthesize the digital controller w.r.t.~the specification on the digital model.  
Finally, in Step~C, the synthesized digital controller is generated.  
The output by \tool~is the synthesized digital controller represented either as a transfer function or in state-space form.  
The synthesis is considered to be \emph{successful} if a digital controller is
correctly synthesized w.r.t. effects of finite precision arithmetic; or if there is no solution (no
controller) for the corresponding physical plant (given the implementation
requirements), then the synthesis is considered to have \emph{failed} \note{we don't seem to have any such instance.}.

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{figures/synthesis-flow.pdf}
\caption{The Digital-System Synthesizer (\tool) tool - distinct phases of the controller synthesis }
\label{fig:synthesis-flow}
\end{figure*}

The implementation of the proposed methodology for synthesis of digital controls for physical plants is based on the Digital-System Synthesizer 
(\tool) tool~\cite{DBLP:conf/kbse/AbateBCCCDKKP17}, 
which can be split into two main stages: manual and automated, as illustrated in Fig.~\ref{fig:synthesis-flow} and detailed next.

The first stage comprises the following steps. 
In Step~1, the user selects the system representation, which can be a transfer function or a state-space model (we focus on the latter in this article).   
In Step~2, the plant (e.g., in the form of Equation~\eqref{eq:ode1}) is provided~\cite{astrom1997computer}.  
Finally, in Step~3, the numerical representation for the digital controller implementation must be set by the user: 
this is the finite-precision arithmetic that defines the number of bits of integer and fractional parts when using fixed-point arithmetic, 
or half- and single-precision when using floating-point arithmetic. 
The user also specifies the input range.

In the second stage, 
the automated synthesis process starts with Step~A, where the
\tool~translates the model specification into an ANSI-C program.  
In Step~B, the discussed CEGIS engine is invoked, 
in order to synthesize the digital controller w.r.t.~the specification given on the model.  
Finally, in Step~C, the synthesized digital controller is generated.  
The output of \tool~is the synthesized digital controller \note{you mean: the closed-loop model}, 
which is represented either as a transfer function or in state-space form (in this article we consider the latter case).  
The synthesis is considered to be \emph{successful} if a digital controller is
correctly synthesized with respect to the effects of finite-precision arithmetic; 
otherwise, if there is no solution (no controller) for the corresponding physical plant (given the implementation requirements), 
then the synthesis is considered to have \emph{failed}.
